Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Avances
Cambios intro

On the other hand, structural adhesives have improved their mechanical properties in recent years and can be now used with confidence in heavy duty applications. Interest on them is also raising up in scientific fields thanks to these enhancements and to the recent development of validated numerical models.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=\linewidth]{./figures/IMG_CUTRES/comparison}
	\caption[Qualitative strength and cost comparison of different joining solutions.]{Qualitative strength and cost comparison of different joining solutions. Taken from \cite{superyacht}.}
	\label{fig:comparison}
\end{figure}

As shown in \Cref{fig:comparison}, adhesives are very competitive both in bonding strength and in economical manufacturing costs \cite{superyacht}. In order to check adhesive's suitability for their use in crashworthy elements, this research develops numerical models of adhesively bonded crash boxes subjected to impact loads using finite element models. Information and data present in the literature are used to create and validate these models in order to ensure the accuracy of the results.

@@

% The methods selected for both the single- and the multi-objective optimization are the genetic algorithms from the JEGA Library, developed by \cite{JEGA}, which perform optimization supporting general constraints as well as mixtures of real and discrete variables.

@@

The force-displacement curve obtained is filtered with a standard SAE 600 filter \cite{J211} before making any calculations, as this removes the high-frequency noise from the curve with a cutoff frequency of ${1000}$ Hz. After this, $E_a$ and $P_{peak}$ are obtained.
% \begin{equation}\label{Ea}
%   E_{a}=\int _{0}^{\delta }F\! \left( z \right) \,dz\,,
% \end{equation}
% where $\delta$ is the total axial crushing distance and $F\! \left( z \right)$ the crushing force at a distance $z$.

% The peak load $P_{peak}$ is defined as
% \begin{equation}\label{Peak}
%  P_{peak}=max\left\{ F\! \left( z \right)  \forall z \in [0,\delta] \right\}
% \end{equation}

@@

% Secondly, single-objective optimization is run for the SEA objective function. Whereas an optimization of the mass and the absorbed energy would provide better results, this can be easier optimized, since the other option requires multi-objective optimization. Both unconstrained and constrained optimization procedures are considered, setting a limit for the peak load constraint in the latter.

>>>>

On the other hand, structural adhesives have improved their mechanical properties in recent years and can be now used with confidence in heavy duty applications. Interest on them is also raising up in scientific fields thanks to these enhancements and to the recent development of validated numerical models.

\begin{figure}[htpb]
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/ace}
    \caption{ACE body structure design by Honda. Relevant structural members and load paths. Taken and modified from \cite{tesis_mcostas}.}
    \label{fig:car}
\end{subfigure}
\qquad
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/energy_absorption2}
    \caption{Schematics of an aircraft fuselage drop test for crashworthiness evaluation. Taken from \cite{Paz:2014dw}.}
    \label{fig:plane}
\end{subfigure}
\label{fig:car_plane}
\end{figure}

% As shown if \cref{fig:car_plane},

\Cref{fig:car,fig:plane} show the schematics of a car frame and a fuselage section, both enclosing crash boxes. For these applications, adhesives are very competitive both in bonding strength and in economical manufacturing costs \cite{superyacht}. In order to check adhesive's suitability for their use in crashworthy elements, this research develops numerical models of adhesively bonded crash boxes subjected to impact loads using finite element models. Information and data present in the literature are used to create and validate these models in order to ensure the accuracy of the results.

@@

@@

The force-displacement curve obtained is filtered with a standard SAE 600 filter \cite{J211} before making any calculations, as this removes the high-frequency noise from the curve with a cutoff frequency of ${1000}$ Hz. After this, $E_a$ and $P_{peak}$ are obtained.

@@
